---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# RobustEM

<!-- badges: start -->
<!-- badges: end -->

The goal of RobustEM is to carry out clustering on high dimensional points using expectation-maximization algorithm which is robust against outliers.

## Usage Example

```{r example, message=FALSE}
library(RobustEM)
```

The example here simulate 720 points belonging to 6 clusters. Each cluster has 120 points. All the points have two dimensions. All the clusters have approximately 6% of points as outliers. The outliers are generated here as having the same mean but a covariance matrix with much larger elements. This customized function `simMultGauss` not only generates the data points but also includes detailed cluster information (mean and covariance of each cluster).

```{r simulatedata, message=FALSE, warning=FALSE}
sim_info <- simMultGauss(n = 120, d = 2, cluster = 6, out_perc = 0.03, out_mag = 4)
```

We can use function `robustEM` to cluster the points.

```{r Cluster, message=FALSE, warning=FALSE} 
result <- robustEM(sim_info[["simdata"]], cluster = 6)
```


I have written a customized summary function to summarize the cluster mean and the number of points in each cluster.

```{r summary}
summary(result)
```
